Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Flow

### 2016-04-27 main.tex
started methods section

>>>>

The Lattice Boltzmann method is a numerical approach that uses statistical mechanics to represent a variety of physical processes, such as fluid flow.
More specifically, LBM can be thought of as a special finite difference discretization of the lattice Boltzmann equation~\cite{chen1998lattice}.
The length scale of LBM is unique in contrast to most common numerical methods, and is referred to as the mesoscale.
In contrast to continuum based methods, LBM simulates the kinetics of microscopic particles, and so it reaches a finer length scale than the macroscopic domain of continuum mechanics; and in contrast to molecular dynamics, discrete element method, and other particle scale approaches, LBM does not deal with a complete description of the degrees of freedom for each individual particle.
LBM instead relies on a statistical description of particle distributions, making LBM, in general, more computationally efficient and requiring less memory than other particle methods.
In addition, the Boltzmann equation is continuous, so LBM inherits the smoothness and stability of continuum methods.
Thus, LBM can be seen as a compromise between continuum and particle methods, combining strengths from each.

LBM has some advantages over other methods of CFD.
For example, LBM is a computationally efficient approach for some CFD.
This efficiency is a consequence of two distinct features of LBM: (1) the convective operator is linear, as opposed to the nonlinear convection terms that appear in continuum mechanics approaches; and (2) the fluid pressure is given by an equation of state.
Solving for the fluid pressure in traditional method sis more computationally expensive and requires special treatment such as iteration and/or relaxation~\cite{chen1998lattice}.
